Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-14 optim.qmd
clean up repo

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(ggh4x)
library(broom)
library(kableExtra)
library(ferrn)
load(here::here("data/sim_pipe.rda"))
load(here::here("data/sim_sine_6d_spline_head.rda"))
load(here::here("data/sim_sine_6d_spline_best.rda"))
load(here::here("data/sim_sine_6d_spline_projdist.rda"))
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
load(here::here("data/sq_basis_dist_idx.rda"))
load(here::here("data/sim_df.rda"))
```

@@

```{r}
#| label = fig-proportion,
#| fig.width = 6,
#| fig.height = 3,
#| fig.align = "center",
#| fig.cap = "Proportion of simulations reaches near-optimal index values in the pipe-finding problem using the holes index. The proportion is calculated based on the number of simulations, out of 50, that achieve an index value within 0.05 of the best-performing simulation. As the dimensionality increases, the proportion of simulations reaching the optimal index value increases."
pipe_run_summ <- sim_pipe |>
  mutate(idx_f = "holes") |>
  group_by(id, n_jellies, max_tries, d) |> 
  summarise(I_max = max(index_val))

pipe_sim_best <- pipe_run_summ |> 
  group_by(n_jellies, max_tries, d) |>
  summarise(I_best = max(I_max))

pipe_res <- pipe_run_summ |> 
  left_join(pipe_sim_best) |> 
  mutate(diff = abs(I_max - I_best) < 0.05) |> 
  group_by(n_jellies, max_tries, d) |> 
  summarise(proportion = sum(diff) / n()) |> 
  mutate(d = as.factor(d), n_jellies = as.factor(n_jellies))

>>>>

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(ggh4x)
library(broom)
library(kableExtra)
library(ferrn)
load(here::here("data/sim_pipe_run_best.rda"))
load(here::here("data/sim_sine_6d_spline_head.rda"))
load(here::here("data/sim_sine_6d_spline_best.rda"))
load(here::here("data/sim_sine_6d_spline_projdist.rda"))
load(here::here("data/pipe_better.rda"))
load(here::here("data/pipe_jellyfish.rda"))
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
load(here::here("data/sq_basis_dist_idx.rda"))
load(here::here("data/sim_df.rda"))
```

@@

```{r}
#| label = fig-proportion,
#| fig.width = 6,
#| fig.height = 3,
#| fig.align = "center",
#| fig.cap = "Proportion of simulations reaches near-optimal index values in the pipe-finding problem using the holes index. The proportion is calculated based on the number of simulations, out of 50, that achieve an index value within 0.05 of the best-performing simulation. As the dimensionality increases, the proportion of simulations reaching the optimal index value increases."
pipe_sim_best <- sim_pipe_run_best |> 
  group_by(n_jellies, max_tries, d) |>
  summarise(I_best = max(I_max))

pipe_res <- sim_pipe_run_best |> 
  left_join(pipe_sim_best) |> 
  mutate(diff = abs(I_max - I_best) < 0.05) |> 
  group_by(n_jellies, max_tries, d) |> 
  summarise(proportion = sum(diff) / n()) |> 
  mutate(d = as.factor(d), n_jellies = as.factor(n_jellies))

### 2024-06-14 optim.tex
clean up repo

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, left=2mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toprule=.15mm, toptitle=1mm, colback=white, colframe=quarto-callout-note-color-frame, titlerule=0mm, breakable, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, bottomtitle=1mm, bottomrule=.15mm, arc=.35mm, rightrule=.15mm, leftrule=.75mm, opacityback=0]

>>>>

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, rightrule=.15mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, opacityback=0, bottomrule=.15mm, titlerule=0mm, breakable, left=2mm, colback=white, toptitle=1mm, bottomtitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toprule=.15mm, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm]
